Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-14 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
went through start of Section 3

\section{Feature Extraction}
\label{sec:features}
Application of machine learning methods to scheduling problems requires careful selection of data describing the hidden dependencies between operations of different jobs \cite{ismail2012production,nasiri2019data}. Clustering methods, which we aim to apply in our approach, are not an exception. Thus, a clustering method requires an informative set of features describing jobs, their operations, and machines of an instance to find patterns resulting in a beneficial decomposition of all operations in time windows.

Methods suggested in the previous work \cite{koonce2000using, harrath2002genetic, shahzad2010discovering, ismail2012production, adibi2014clustering, nasiri2019data} used characterizations of scheduling instances based on the following features: priority, processing time, remaining processing time, machine load, and route position. 
Most of the approaches converted the quantitative values of the attributes into qualitative data. As mentioned in these studies, the main reason for this conversion was to make the heuristic dispatching rules more generic and allow their application to several scheduling problems. 
In this work, we suggest a method that can work directly on the sets of features and does not require any problem-specific transformations. However, our clustering method for JSP instance decomposition requires all features to have numerical values allowing distance measures to estimate similarities/dissimilarities between operations of jobs.
%
Therefore, we suggest the following features:
\begin{description}
  \item[Processing Time (PT)] that represents the execution time of a particular operation in a machine. This feature is provided in every JSP instance, like in the sample instance presented in Table \ref{tab1}.

@@

\begin{table}[h!]
\setlength{\tabcolsep}{10.0pt}
\centering
  \begin{center}
  \caption{Features extracted for the sample problem instance.}
  \label{tab3}
 %\begin{adjustwidth}{0.0cm}{}
    \begin{tabular}{c  c  c  c  c  c}
      \textbf{Operation} & \textbf{RPT} & \textbf{EST} & \textbf{ML} & \textbf{\stfifo} & \textbf{\wtfifo}\\
      \hline
										\\
      $O_{1,1}$  & 17 & 0   & 20	&  0  & 0\\
      $O_{1,2}$  & 8  & 9   & 3		&  9  & 0\\
      $O_{1,3}$  & 5  & 12  & 5	  &  12 & 0\\
										\\
      $O_{2,1}$  & 12 & 0   & 10	&  0  & 0\\
      $O_{2,2}$  & 8  & 4   & 11	&  9  & 5\\
      $O_{2,3}$  & 2  & 10  & 7	  &  17 & 2\\
					    					\\
      $O_{3,1}$  & 12 & 0  & 11	  &  0  & 0\\
      $O_{3,2}$  & 8  & 4  & 6		&  4  & 0\\
      $O_{3,3}$  & 5  & 7  & 5		&  15 & 8\\
    \end{tabular}
%\end{adjustwidth}

@@

\section{Proposed Algorithm}
\label{sec:method}
In this section, we will show the implementation of our proposed model and how it works. The main idea of the proposed model is to split the problem into sub-problems, solve them sequentially and integrate the solutions to have the solution of the main problem. We aim to decompose the problem into TWs because this technique proved its effectiveness for solving the scheduling problems \cite{zhang2010hybrid,zhai2014decomposition}. Several ways have been presented during the last decades to decompose the problem \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}.\\

>>>>

\section{Feature Extraction}
\label{sec:features}
The application of machine learning methods to scheduling problems requires a careful selection of data describing the hidden dependencies between operations of different jobs \cite{ismail2012production,nasiri2019data}. Clustering methods, which we intend to apply in our approach, are not an exception to this. That is, a clustering method requires an informative set of features characterizing the jobs, their operations, and machines of a problem instance to identify patterns resulting in a beneficial decomposition of the operations into time windows.

Methods suggested in the literature \cite{koonce2000using, harrath2002genetic, shahzad2010discovering, ismail2012production, adibi2014clustering, nasiri2019data} characterize instances of scheduling problems based on the following features: priority, processing time, remaining processing time, machine load, and sequence position. 
Most of these approaches convert the quantitative feature values % of the attributes
into qualitative attributes in order to obtain generic dispatching rules
that remain applicable to instances of different size.
% As mentioned in these studies, the main reason for this conversion was to make the heuristic dispatching rules more generic and allow their application to several scheduling problems. 
In this work, we propose a method that can be applied to feature values directly and does not require any problem-specific transformations. However, our clustering method for JSP instance decomposition requires all features to have numerical values, which permit the calculation of distance measures for estimating (dis)similarities between operations.

In detail, we consider the following features of jobs, operations, and machines:
\begin{description}
  \item[Processing Time (PT)] that represents the execution time of a particular operation in a machine. This feature is provided in every JSP instance, like in the sample instance presented in Table \ref{tab1}.

@@

\begin{table}[t]
\setlength{\tabcolsep}{10.0pt}
\centering
  \begin{center}
  \caption{Features extracted for the sample problem instance from Table~\ref{tab1}.}
  \label{tab3}
 %\begin{adjustwidth}{0.0cm}{}
    \begin{tabular}{c  c  c  c  c  c}
      \textbf{Operation} & \textbf{RPT} & \textbf{EST} & \textbf{ML} & \textbf{\stfifo} & \textbf{\wtfifo}\\
      \hline
										\\
      $O_{1,1}$  & 17 & 0   & 20	&  0  & 0\\
      $O_{1,2}$  & 8  & 9   & 3		&  9  & 0\\
      $O_{1,3}$  & 5  & 12  & 5	  &  12 & 0\\
										\\
      $O_{2,1}$  & 12 & 0   & 10	&  0  & 0\\
      $O_{2,2}$  & 8  & 4   & 11	&  9  & 5\\
      $O_{2,3}$  & 2  & 10  & 7	  &  17 & 2\\
					    					\\
      $O_{3,1}$  & 12 & 0  & 11	  &  0  & 0\\
      $O_{3,2}$  & 8  & 4  & 6		&  4  & 0\\
      $O_{3,3}$  & 5  & 7  & 5		&  15 & 8\\
    \end{tabular}
%\end{adjustwidth}

@@

\section{Constrained Clustering Algorithm}
\label{sec:method}
In this section, we will show the implementation of our proposed model and how it works. The main idea of the proposed model is to split the problem into sub-problems, solve them sequentially and integrate the solutions to have the solution of the main problem. We aim to decompose the problem into TWs because this technique proved its effectiveness for solving the scheduling problems \cite{zhang2010hybrid,zhai2014decomposition}. Several ways have been presented during the last decades to decompose the problem \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}.\\
